|

### 2022-07-25 manuscript.Rmd
better manage figures in figure directory

```{r setup, include=FALSE, echo=FALSE, purl=FALSE}
knitr::opts_chunk$set(echo = FALSE)

@@

>>>>

```{r setup, include=FALSE, echo=FALSE, purl=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.path = "figure/")

@@

<!-- ```{r manual-alt, fig.cap = "Figure caption.", fig.alt = "Alt text."} -->
# knitr::include_graphics("path/to/file.png")
<!-- ``` -->
